### 2022-11-15 NSF2022/Description/priorsupport.tex

\begin{comment}
\begin{wrapfigure}[11]{r}{0.56\textwidth}
\vspace{-19pt}
%\definecolor{barblue}{RGB}{51,102,254}
%\renewcommand\sfdefault{phv}
%\renewcommand\mddefault{mc}
%\renewcommand\bfdefault{bc}
%\sffamily
\begin{ganttchart}[
    canvas/.append style={fill=none, draw=black!5, line width=.75pt},
        x unit =4.5mm,
        y unit chart =\baselineskip,
    hgrid style/.style={draw=black!5, line width=.75pt},
    vgrid={*1{draw=black!5, line width=.75pt}},
    title/.style={draw=none, fill=none},
    title label font=\bfseries\footnotesize, % numbers across the top
    title label node/.append style={below=3pt},
    include title in canvas=false,
    bar label font=\mdseries\footnotesize\color{black!70}, 
    % titles across the left
    %bar label node/.append style={left=2cm},
    bar/.append style={draw=none, fill=blue},
    bar incomplete/.append style={fill=blue},
    bar progress label font=\mdseries\footnotesize\color{black!70},
    milestone label font=\mdseries\small\color{black!70},
        milestone left shift =0.9,
        milestone right shift =0.1,
        % Don't draw group bars
        group height =0,
        group peaks height =0,
        group label font =\bfseries\small,
]{1}{12}
\gantttitle[
    title label node/.append style={below left=3pt and -6pt}
]{QUARTERS:\quad1}{1}
\gantttitlelist{2,...,12}{1} \\
%\ganttgroup{Tasks\hfill}{1}{12}\\
\ganttbar[bar/.append style={fill=red}]{Specific Aim 1}{1}{12} \\
\ganttbar[bar/.append style={fill=blue}]{Specific Aim 2}{1}{12}\\
\ganttbar[bar/.append style={fill=green}]{Specific Aim 3}{1}{12}\\
\ganttbar[bar/.append style={fill=black}]{Program Management}{1}{12}
\ganttbar[bar/.append style={fill=magenta}]{}{4}{4}
\ganttbar[bar/.append style={fill=magenta}]{}{8}{8}
\ganttbar[bar/.append style={fill=magenta}]{}{12}{12}
\end{ganttchart}
\vspace{-10pt}
\caption{Schedule for the proposed work, measured in quarters from the
  beginning of the project. The lead PI of each Specific Aim will be
  Ryham (red), Quaife (blue), and Young (green). Project management will
  be continuous (black), but we anticipate extra attention will be
  necessary to align objectives in quarters 4, 8, and 12 (magenta).}
\label{fig:schedule}
\end{wrapfigure}
\end{comment}
\textbf{Project management}: 
%
The success of the proposed research requires complementary expertise
and collaborative efforts in physics, applied mathematics, and
scientific computing. PI Ryham has been working on mathematical modeling
with a strong analytical background. PI Young has been working on many
areas of fluid dynamics with applications to soft matters. 
PI Quaife has been working on integral equation methods,
fast algorithms, and their applications to fluid dynamics.  
Their recent collaborative works on the granule-based vesicles
in two dimensions~\cite{FuQuRyYo22, fu-ryh-qua-you2022} has provided a
solid foundation for the proposed research.

\smallskip

\textbf{Collaboration plan}: 
%
PI Quaife is responsible for the overall management of the project.
The research work is structured to meet the tasks
in \S\ref{sec:proposed-work}. The PIs and students will meet
on Zoom and in person when possible. PI Ryham and PI Young
will conduct biweekly meetings in person, with PI Quaife joining over
Zoom from Florida. The PIs will share software packages, paper sources,
and references on a common \textsf{Git} repository. The resulting
software packages will be posted on the \textsf{Github} software
repository.
%
%\smallskip
%
\textbf{Research Schedule:} The detailed schedule for the proposed work
is shown in Figure~\ref{fig:schedule}. Each PI will spearhead a
Specific Aim, and program management will happen
throughout, with special coordination taken in quarters 4, 8, and
12.

>>>>

\begin{comment}
\begin{wrapfigure}[11]{r}{0.56\textwidth}
\vspace{-19pt}
%\definecolor{barblue}{RGB}{51,102,254}
%\renewcommand\sfdefault{phv}
%\renewcommand\mddefault{mc}
%\renewcommand\bfdefault{bc}
%\sffamily
\begin{ganttchart}[
    canvas/.append style={fill=none, draw=black!5, line width=.75pt},
        x unit =4.5mm,
        y unit chart =\baselineskip,
    hgrid style/.style={draw=black!5, line width=.75pt},
    vgrid={*1{draw=black!5, line width=.75pt}},
    title/.style={draw=none, fill=none},
    title label font=\bfseries\footnotesize, % numbers across the top
    title label node/.append style={below=3pt},
    include title in canvas=false,
    bar label font=\mdseries\footnotesize\color{black!70}, 
    % titles across the left
    %bar label node/.append style={left=2cm},
    bar/.append style={draw=none, fill=blue},
    bar incomplete/.append style={fill=blue},
    bar progress label font=\mdseries\footnotesize\color{black!70},
    milestone label font=\mdseries\small\color{black!70},
        milestone left shift =0.9,
        milestone right shift =0.1,
        % Don't draw group bars
        group height =0,
        group peaks height =0,
        group label font =\bfseries\small,
]{1}{12}
\gantttitle[
    title label node/.append style={below left=3pt and -6pt}
]{QUARTERS:\quad1}{1}
\gantttitlelist{2,...,12}{1} \\
%\ganttgroup{Tasks\hfill}{1}{12}\\
\ganttbar[bar/.append style={fill=red}]{Specific Aim 1}{1}{12} \\
\ganttbar[bar/.append style={fill=blue}]{Specific Aim 2}{1}{12}\\
\ganttbar[bar/.append style={fill=green}]{Specific Aim 3}{1}{12}\\
\ganttbar[bar/.append style={fill=black}]{Program Management}{1}{12}
\ganttbar[bar/.append style={fill=magenta}]{}{4}{4}
\ganttbar[bar/.append style={fill=magenta}]{}{8}{8}
\ganttbar[bar/.append style={fill=magenta}]{}{12}{12}
\end{ganttchart}
\vspace{-10pt}
\caption{Schedule for the proposed work, measured in quarters from the
  beginning of the project. The lead PI of each Specific Aim will be
  Ryham (red), Quaife (blue), and Young (green). Project management will
  be continuous (black), but we anticipate extra attention will be
  necessary to align objectives in quarters 4, 8, and 12 (magenta).}
\label{fig:schedule}
\end{wrapfigure}
\end{comment}
PI Quaife is responsible for the overall management of the project.
The research work is structured to meet the tasks
in \S\ref{sec:proposed-work}. The PIs and students will meet
by video conference and in person when possible. PI Ryham and PI Young
will conduct biweekly meetings in person, with PI Quaife joining over
video conference from Florida. The PIs will share software packages, paper sources,
and references on a common \textsf{Git} repository. The resulting
software packages will be posted on the \textsf{Github} software
repository.
%
%\smallskip
%
The detailed schedule for the proposed work
is shown in Figure~\ref{fig:schedule}. Each PI will spearhead a
Specific Aim, and program management will happen
throughout, with special coordination taken in quarters 4, 8, and
12.
